SSA based global code motion of identical computations

### 2017-04-14 hoist.tex
remove verbose dfsin arguments

\subsubsection{Partition the list of hoisting candidates to maximize hoisting}
\label{subsec:partition}
In order to hoist a subset of identical instructions, we partition the list of
all candidates in a way to maximize the total number of hoistings.  By sorting
the list of all the candidates in the increasing order of their depth first
search discovery time stamp \cite{clrs} (DFSIn numbers), we make sure that
candidates closer in the list have their common dominator nearby in cases when
there are no fully redundant instructions. In Figure-\ref{fig:dfsin}, if B3 B4
B5 and B6 have identical computations and for some reason they cannot be hoisted
together at B0, then we partition the set of hoistable candidates in their DFSin
order.

@@

So by sorting candidates w.r.t. their DFSIn numbers:
\begin{enumerate}
\item would make fewer checks for legality and profitability.
\item hoisting point will be closer, so the intersection of live-range of the
  instruction with other instructions will be minimal.
\end{enumerate}

In our current implementation we keep as many candidates in one set as possible
(greedy approach). We split the list at a point where the legality checks fail
to hoist subset of candidates which are legal to hoist and then start finding
new hoisting point for the remaining ones. So there are two limitations of the
current implementation of the partition algorithm: first, sorting by DFSIn
numbers does not give the desired order when there are fully redundant
instructions; second, it lacks cost model for partitioning in order to
preserve/improve performance, see Section~\ref{sec:future-work}.

>>>>

\subsubsection{Partition the list of hoisting candidates to maximize hoisting}
\label{subsec:partition}
In order to hoist a subset of identical instructions, we partition the list of
all candidates in a way to maximize the total number of hoistings.  By sorting
the list of all the candidates in the increasing order of their depth first
search discovery time stamp \cite{clrs} (DFSIn numbers), we make sure that
candidates closer in the list have their common dominator nearby. In
Figure-\ref{fig:dfsin}, if B3, B4, B5, and B6 have identical computations and for
some reason they cannot be hoisted together at B0, then we partition the set of
hoistable candidates in their DFSIn order. In this case the DFSIn ordering would
be B3, B4, B5, B6 which will allow the instructions in B3, B4 to be hoisted at
B1 and those in B5, B6 to be hoisted at B2.

@@

In our current implementation we keep as many candidates in one set as possible
(greedy approach). We split the list at a point where the legality checks fail
to hoist subset of candidates which are legal to hoist and then start finding
new hoisting point for the remaining ones.
